\documentclass[a4paper,10pt]{article}

\usepackage{fontspec}
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Gill Sans Light]
{Gill Sans Light}

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

% \usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}

\usepackage{fullpage}
\usepackage{microtype}

% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage[
pdfauthor={Pedro E. M. Brito},
pdftitle={Pedro Brito's résumé}]
{hyperref} 
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{tabularx}

\usepackage{fontspec}
\makeatletter
\newlength\fake@f
\newlength\fake@c
\def\fakesc#1{%
  \begingroup%
  \xdef\fake@name{\csname\curr@fontshape/\f@size\endcsname}%
  \fontsize{\fontdimen8\fake@name}{\baselineskip}\selectfont%
  \uppercase{#1}%
  \endgroup%
}
\makeatother

\renewcommand{\textsc}{\fakesc}

\begin{document}

\pagestyle{empty} % Removes page numbering

\par{\centering{\Huge Pedro Brito}\bigskip\par}

\section{Personal Info}

\begin{tabularx}{\textwidth}{ rl}
  \textsc{Full name:} & Pedro Emilio Machado de Brito \\
  \textsc{Phone:}  & +55 (19) 99873-0963 \\
  & +55 (31) 99433-0100 \\
  \textsc{Email:} & \href{mailto:pedroembrito@gmail.com}{pedroembrito@gmail.com}\\
%  \footnotesize{pemb @} & \href{https://github.com/pemb/}{GitHub}, \href{https://bitbucket.org/pemb}{Bitbucket}, \href{https://gitlab.com/pemb}{GitLab}\\
\end{tabularx}

% \section{Summary}

% An efficient and meticulous programmer on one side, relentless problem solver
% and debugger on the other, with a good background in algorithms and data
% structures, experience with debugging tools and techniques, as well as knowledge
% of other development tools such as version control systems, build automation and
% profiling.

% I'm eager to work on high performance (possibly parallel) software, especially where knowledge of the underlying architectural issues is essential to good results. I'm also interested in FPGA programming and kernel development.

\section{Work}

\begin{tabularx}{\textwidth}{r|X}	

  \emph{February 2017} & \textbf{Software Engineering internship} at \textbf{Google}, in Belo Horizonte, Minas Gerais, Brazil.\\
  \textsc{August 2016} & {\footnotesize Worked on the \href{https://play.google.com/store/apps/details?id=com.google.android.apps.kids.familylink}{Family Link Android} app, as well as on server-side and infrastructure development}.\\

\end{tabularx}

\section{Education}

\begin{tabularx}{\textwidth}{r|X}

  \emph{July 2017} & Bachelor of \textbf{Computer Science} from \textbf{Unicamp}, in Campinas, São Paulo, Brazil.\\
  \textsc{2012} & {\footnotesize Took leave of absence during exchange program and internship.}  \\

  \multicolumn{2}{c}{}\\

  \emph{May 2016} & \textbf{Computer Science} exchange student at \textbf{Vanderbilt University}, in Nashville, Tennessee. \\
  \textsc{August 2015} & {\footnotesize as a Brazilian Scientific Mobility Program (Ciência sem Fronteiras) grantee.}  \\

\end{tabularx}

\section{Academic}

%\begin{tabular}{r|p{11cm}}
\begin{tabularx}{\textwidth}{r|X}

  \emph{July 2016} & \textbf{Summer Undergraduate Engineering Research Immersion Program}\\
 \textsc{May 2016}  & at the \textbf{Illinois Institute of Technology}, in Chicago, Illinois, under \href{https://engineering.iit.edu/faculty/jafar-saniie}{\emph{Dr. Jafar Saniie}}\\
                     &{\footnotesize Developed a simple FPGA-based cryptography acceleration module for the Zynq SoC.}\\
  \multicolumn{2}{c}{} \\


  \emph{August 2015} & \textbf{Undergraduate research project} at Unicamp\\
  \textsc{February 2015} & under \href{http://www.ic.unicamp.br/~cortes/}{\emph{Prof. Mario L. Côrtes}} and \href{http://guidoaraujo.wordpress.com/}{\emph{Prof. Guido Araújo}}\\
                     & {\footnotesize Investigated security issues involving memory integrity in embedded devices, with IoT applications.}\\
  \multicolumn{2}{c}{} \\

  \emph{2013 -- 2015} & \textbf{Undergraduate T.A.} in undergraduate classes at Unicamp \\
  \textsc{H1 2015} & {\footnotesize Digital Circuits Laboratory, under \href{http://guidoaraujo.wordpress.com/}{\emph{Prof. Guido Araújo}}}\\
  \textsc{H2 2014} & {\footnotesize Logic Circuits and Computer Organization, under \href{http://www.ic.unicamp.br/~cortes/}{\emph{Prof. Mario L. Côrtes}}}\\
  \textsc{H2 2013} & {\footnotesize Data Structures, under \href{http://ic.unicamp.br/~gpt/}{\emph{Prof. Guilherme P. Telles}}}\\
  \multicolumn{2}{c}{}\\

  \emph{2012 -- 2015} & Positions at \href{http://www.caco.ic.unicamp.br}{CACo} \footnotesize{(the Computing Students' Union at Unicamp)} \\
  \textsc{2014 -- 2015} & {\footnotesize \textbf{Financial coordinator}: Handled bookkeeping, payments to suppliers, and other financial matters.}\\
  \textsc{2013 -- 2014} & {\footnotesize \textbf{President}: Held weekly meetings, managed projects and events, and carried out administrative tasks.}\\
  \textsc{2012 -- 2013} & {\footnotesize \textbf{Tech coordinator}: Managed small servers, deployed a webcam surveillance system.}\\

%\end{tabular}
\end{tabularx}

\section{Knowledge and experience}

\begin{tabular}{rl}
  Fair: &  Java, C, Python, Android, GNU/Linux, Unix tools, algorithms, data structures, threading and concurrency\\\\

  Basic: &  C++, git, make, shell scripting, OpenMP, ARM assembly, VHDL, {\fontfamily{lmr}\selectfont \LaTeX}, newtorking, system administration\\
\end{tabular}

\section{Languages}

\begin{tabularx}{\textwidth}{rXr}
  \textbf{English:} & Fluent. \\
  \textbf{Portuguese:} & Native language.\\
\end{tabularx}

\end{document}
